### 2019-03-24 Sections/cryptowars.tex
Dad's quotes
Minor formatting

However, this is not to say that QKD is actually perfectly secure in real life. Recent history has demonstrated that this is certainly not the case, with many attacks against various quantum cryptographic protocols being described and successfully demonstrated. The reason for this schism between theory and experiment is that no experiment ever \textit{perfectly} mimics the theoretical proposal it is trying to implement. Laboratory components might be imprecise in an unfortunate way, opening up avenues for attack, or they might perform unwanted additional actions that leak information to Eve. The prospects for such so-called `side-channel attacks'\index{Side-channel attacks} must be carefully considered and satisfactorily addressed.

@@

\subsection{Beamsplitter and photon-number-splitting attacks}\index{Beamsplitter attacks}\index{Photon-number-splitting attacks}

>>>>

However, this is not to say that QKD is actually perfectly secure in real-life. Recent history has demonstrated that this is certainly not the case, with many attacks against various quantum cryptographic protocols being described and successfully demonstrated. The reason for this schism between theory and experiment is that no experiment ever \textit{perfectly} mimics the theoretical proposal it is trying to implement. Laboratory components might be imprecise in an unfortunate way, opening up avenues for attack, or they might perform unwanted additional actions that leak information to Eve. The prospects for such so-called `side-channel attacks'\index{Side-channel attacks} must be carefully considered and satisfactorily addressed.

@@

\subsection{Beamsplitter \& photon-number-splitting attacks}\index{Beamsplitter attacks}\index{Photon-number-splitting attacks}

### 2019-03-24 Sections/economics_of_the_quantum_internet.tex
Minor formatting

\dropcap{O}{ur} analysis thus far has been very theoretical. But our observations have very tangible implications in the real world. This has implications for governments, regulatory authorities, fiscal and technology policy, national security, and any end users of the quantum cloud.

@@

It's important to note that these values are totally arbitrary in nature, and do not have a `real life' interpretation, other than understanding the preferencing of the described strategies. Translating the utility payoff matrix into a graphical representation yields Fig.~\ref{fig:game_theory_2}.

>>>>

\dropcap{O}{ur} analysis thus far has been very theoretical. But our observations have very tangible implications in the real-world. This has implications for governments, regulatory authorities, fiscal and technology policy, national security, and any end users of the quantum cloud.

@@

It's important to note that these values are totally arbitrary in nature, and do not have a `real-life' interpretation, other than understanding the preferencing of the described strategies. Translating the utility payoff matrix into a graphical representation yields Fig.~\ref{fig:game_theory_2}.
